---
title: "Exercise 2-Burritos!"
author: "Matt Savoca"
date: "`r Sys.Date()`"
output: 
  github_document 

---
```{r}
knitr::opts_chunk$set(echo=FALSE)
```



```{r load-packages, message=FALSE}
library(tidyverse)
```

# The data

## Kaggle: SD Burritos

The data come from [Kaggle.com](https://www.kaggle.com/srcole/burritos-in-san-diego):

>Mexican cuisine is often the best food option is southern California. And the 
>burrito is the hallmark of delicious taco shop food: tasty, cheap, and filling. 
>Appropriately, an effort was launched to critique burritos across the county 
>and make this data open to the lay burrito consumer. 

```{r load-data, warning=FALSE, collapse=TRUE}
burritos <- read_csv("burritos_01022018.csv")
```


## About the data

At this time, the data set contains ratings from over `r nrow(burritos)` 
burritos fromd `r burritos %>% count(Location) %>% nrow()` restaurants.

There are 10 core dimensions of the San Diego burrito:

 1. Volume 
 1. Tortilla quality 
 1. Temperature 
 1. Meat quality 
 1. Non-meat filling quality 
 1. Meat-to-filling ratio 
 1. Uniformity 
 1. Salsa quality 
 1. Flavor synergy 
 1. Wrap integrity

All of these measures (except for Volume) are rated on a scale from 0 to 5, 0 
being terrible, and 5 being optimal. Other information available for each 
burrito includes an overall rating, cost, Yelp rating of the restaurant, and more.

## Glimpse at the data

```{r allows_examining_of_data, results='hide'}
glimpse(burritos)
```
I have results='hide' in above chunk to not show a long and nasty str table

# Slicing large dataframe to top 50 rows
```{r}
burritos_short = slice(burritos, 1:50)
```


# Exploratory data analysis

## Reviewer counts

First let's take a look at who the reviewers are:

```{r reviewers_and_number_of_burritos_they_ate}
burritos_rev_count <- burritos %>%
  mutate(Reviewer = fct_lump(Reviewer, n = 5)) %>%
  count(Reviewer) %>%
  mutate(Reviewer = fct_reorder(Reviewer, n, .desc = TRUE)) %>%
  arrange(desc(n))
burritos_rev_count
ggplot(data = burritos_rev_count, mapping = aes(x = Reviewer, y = n)) +
    geom_bar(stat = "identity") +
    labs(title = "Distribution of reviewers", x = "", y = "")
```

Seems like `r burritos_rev_count$Reviewer[1]`  has been eating a lot of burritos!


## Overall rating vs. cost

Next we visualize the relationship between the cost and overall rating of the 
burritos. The relationship appears to be positive, though the one extremely 
expensive burrito makes it difficult to assess the strength of the relationship.

```{r scatterplot_of_rating_vs_cost, collapse=TRUE, fig.cap="SRS"}
ggplot(data = burritos, mapping = aes(x = Cost, y = overall)) +
  geom_point() +
  labs(title = "Overall rating vs. cost", y = "Overall rating")
```

How is "fig.cap" different than just adding a line at the end of a figure-producing chunk??

# Adding my own plot
```{r}
ggplot(data = burritos, mapping = aes(x = Yelp, y = Google)) +
  geom_point()
```




