---
title: "Get that burrito"
author: "Dr. Savage"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r}
knitr::opts_chunk$set(echo=FALSE)
```



```{r load-packages, message=FALSE}
library(tidyverse)
```

---

# The data

## Kaggle: SD Burritos

The data come from [Kaggle.com](https://www.kaggle.com/srcole/burritos-in-san-diego):

>Mexican cuisine is often the best food option is southern California. And the 
>burrito is the hallmark of delicious taco shop food: tasty, cheap, and filling. 
>Appropriately, an effort was launched to critique burritos across the county 
>and make this data open to the lay burrito consumer. 

```{r load-data, warning=FALSE, collapse=TRUE, include=FALSE}
burritos <- read_csv("burritos_01022018.csv")
```

---

## About the data

At this time, the data set contains ratings from over `r nrow(burritos)` 
burritos fromd `r burritos %>% count(Location) %>% nrow()` restaurants.

There are 10 core dimensions of the San Diego burrito:

 1. Volume 
 1. Tortilla quality 
 1. Temperature 
 1. Meat quality 
 1. Non-meat filling quality 
 1. Meat-to-filling ratio 
 1. Uniformity 
 1. Salsa quality 
 1. Flavor synergy 
 1. Wrap integrity

All of these measures (except for Volume) are rated on a scale from 0 to 5, 0 
being terrible, and 5 being optimal. Other information available for each 
burrito includes an overall rating, cost, Yelp rating of the restaurant, and more.

---

# Exploratory data analysis

## Reviewer counts

First let's take a look at who the reviewers are:
---

```{r reviewers_and_number_of_burritos_they_ate}
burritos_rev_count <- burritos %>%
  mutate(Reviewer = fct_lump(Reviewer, n = 5)) %>%
  count(Reviewer) %>%
  mutate(Reviewer = fct_reorder(Reviewer, n, .desc = TRUE)) %>%
  arrange(desc(n))
burritos_rev_count
```
---
```{r}
ggplot(data = burritos_rev_count, mapping = aes(x = Reviewer, y = n)) +
    geom_bar(stat = "identity") +
    labs(title = "Distribution of reviewers", x = "", y = "")
```


Seems like `r burritos_rev_count$Reviewer[1]`  has been eating a lot of burritos!

[That's what she said](https://media.giphy.com/media/IJLVLpZQuS4z6/giphy.gif)

---
